\documentclass{article}
\usepackage[utf6]{inputenc}
\begin{docuement}

\title{Anthony’s Ending}

\textbf{Alternative Ending}

Milo runs away from the protestors and seeks a safe shelter. In South Hall, Milo redresses himself. His supporter brought a pair of basketball shorts, a UC Berkeley t-shirt and a baseball cap, so Milos can conceal his identity if there is a major threat to his safety. Now Milos looks like a regular UC Berkeley student. By the time Milos walked out of South Hall, unnoticed, it was almost 11’O clock. Students poured out of classes from Wheeler, Dwinelle and from all directions. Meanwhile a campus-wide protest against Milo and Free Speech Week spread .Within minutes Milos was surrounded by protesters. Among screaming crowds, Milos stands quiet, emotionally disturbed and agitated. Feeling very frustrated, Milos picks up his emergency phone and instructs an orders for his battalions to engage in plan B.  Scared Milo ran out of South Hall hides in a gender neutral restroom.\\

\textbf{neigh…neigh…}

Milos hears hissing sound in the bathroom. Outside the bathroom window, he sees a unicorn with a black glossy horn. Mesmerized by the aesthetics of the unicorn’s horn, Milo tries to make an eye contact with the unicorn, The black glossy horn of an unicorn reminds him of his past “acquaintance” he met in a BCR networking event.  After a while, the unicorn notices Milo’s presence and is annoyed by Milo’s attention. Without a warning, the unicorn dashes into the bathroom wall. The black horn easily crumbled concrete walls as if a sharp obsidian knife penetrates gray jello. Meanwhile, Milo is undisturbed by the unicorn’s aggressive behavior. He lets the unicorn penetrate into him. The unicorn stabs his horn into Milo’s torso, but surprisingly, he didn’t feel any pain. Milo, also surprised, looked at himself in the mirror and saw black hemorrhage soaking his shorts.\\

\textbf{the truth reveals}
The unicorn turned away and walked out the bathroom, leaving Milo bleeding for hours. The black blood covered the floor. The unicorn, with his legs and horn stained with Milo’s black blood, walks into strawberry creek to wash himself. The blood not only stained plants drinking the water from strawberry creek, but also stained the concrete walls. Unconfirmed sources say the red autumn foliage and brick color of South Hall come from the blood of Milos. And the reddish hue in some of the campus buildings still remain today. \\


\end{document}
